Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/proofs.tex
Minor change in proofs.

In this section we will prove all theorems we have stated so far.
We observe that the non-interference claims for the languages
|specLang seqf targetLang| and |specLang roundrobinf targetLang|
in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
respectively, about restricted IFC languages where the set
of predicates is the set of always valid predicates.

>>>>

In this section we prove all theorems we have stated.
We first observe that the non-interference claims for the languages
|specLang seqf targetLang| and |specLang roundrobinf targetLang|
in Theorems~\ref{thm:rr-tsni} and~\ref{thm:seq-tini} follow directly
from Theorems~\ref{thm:iso-tsni} and~\ref{thm:iso-tini},
respectively, where the set
of predicates is the set of always valid predicates.
